---
title: "Litigation Summary"
output:
  word_document:
    reference_docx: AwesomeRmarkdownWordReport.docx
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library(knitr)
library(officedown)
library(officer)
library(ggplot2)
library(tidyverse)
library(broom)
library(flextable)
library(scales) # to access break formatting functions

# set chunks defaults
knitr::opts_chunk$set(
  echo       = FALSE,
  message    = FALSE,
  warning    = FALSE
)
# set flextable defaults
knitr::opts_chunk$set(echo = TRUE, fig.cap = TRUE)
  set_flextable_defaults(
  font.family = "Arial", font.size = 9, 
  theme_fun = "theme_vanilla",
  big.mark="", table.layout="autofit")
  
# formatting properties for specific paragraphs
centeredP <- fp_par(text.align = "center")
```
# Introduction

This document includes information regarding the selected litigation cases. A general overview of the cases and metrics reflecting the success of the firm are included.

# Data

This dataset contains data from selected cases. 

```{r data, echo = FALSE,eval=T}
 values$selectedcases %>% dplyr::select(case_name,attorney1,case_type,
                                        date_of_assignment, date_of_resolution,
                                        offer_amt_998, offer_accept_998,
                                        settlement_authority, actual_settlement) %>% 
flextable() %>% autofit()
run_pagebreak()
```

# Settlement Analysis

```{r settlement analysis, echo = FALSE, fig.width = 7, fig.height=7}

values$selectedcases %>% make_long() %>% plot_settlements()

values$selectedcases$date_of_assignment <- as.Date(values$selectedcases$date_of_assignment, "%Y-%m-%d")
values$selectedcases$date_of_resolution <- as.Date(values$selectedcases$date_of_resolution, "%Y-%m-%d")
values$selectedcases$datedur <- difftime(values$selectedcases$date_of_resolution,values$selectedcases$date_of_assignment, units = "days")
avgdur <- mean(values$selectedcases$datedur)

```
**Total savings:** `r format(as.integer(sum(values$selectedcases$savings, na.rm=T)), nsmall=1, big.mark=",")`

**Percent of authority:** `r scales::percent(as.integer(sum(values$selectedcases$actual_settlement))/sum(values$selectedcases$settlement_authority), accuracy = 0.1)`

**Average duration of case:** `r round(avgdur,1)` days


# Notes

(Add any additional notes here)

